
\section{Chain conditions}

Let $A$ be a ring. In this section we focus our attention on ascending chains of ideals of $A$, that is to say, chains of the form $I_1 \subset I_2 \subset \cdots I_n \subset \cdot$; as well as on descending chains $I_1 \subseteq I_2 \subseteq \cdots I_n \subseteq \cdots $

\subsection{Noetherian rings}

\begin{prop}
	Let $A$ be a ring. The following conditions are equivalent:
	\begin{enumerateprop}
		\item \emph{Finite generation}: every ideal $I \subset A$ is finitely generated.
		\item \emph{Ascending chain condition}: every ascending chain $I_1 \subseteq I_2 \subseteq \cdots \subseteq I_n \subseteq \cdots$ of ideals of $A$ stabilises, that is, there exists $m \geq 1$ such that $I_m = I_n$ for all $n \geq m$.
		\item \emph{Maximality}: every non-empty set of ideals of $A$ has a maximal element with respect to inclusion.
	\end{enumerateprop}
\end{prop}
\begin{proof}
	contenidos...
\end{proof}

\begin{definition}
	A ring $A$ is \emphdef{Noetherian} if it satisfies the conditions of the previous proposition.
\end{definition}


\begin{theorem}[Hilbert's basis theorem]
	If $A$ is a Noetherian ring, then $A[x]$ is also Noetherian.
\end{theorem}

\subsection{Artinian rings}

\begin{prop}
	Let $A$ be a ring. The following conditions are equivalent:
	\begin{enumerateprop}
		\item \emph{Descending chanin condition}: every descending chain $I_1 \supseteq I_2 \supseteq \cdots \supseteq I_n \supseteq \cdots$ of ideals of $A$ stabilises, that is, there exists $m \geq 1$ such that $I_m = I_n$ for all $n \geq m$.
		\item \emph{Minimality}: every non-empty set of ideals of $A$ has a minimal element with respect to inclusion. 
	\end{enumerateprop}
\end{prop}

\begin{definition}
	A ring $A$ is \emphdef{Artinian} if it satisfied the conditions of the previous proposition.
\end{definition}




